Understanding the technological transition based on cultural transmission biases during the Late Pleistocene in Korea

### 2020-05-26 analysis/paper/paper.Rmd
add more sentences

biological concept to archaeological usage: (Richerson and Boyd 1992)

Cultrual evolution that archaeologists adapted has three sub-categories: human behavioral ecology, phylogenetics and cultural transmission theory (Garvey 2018). Among them, we apply models and methods of cultural tranmssion to understand the technological change and socio cultural contexts.

@@

Bettinger and Eerkens (1997; 1999; 2008) have shown how these biases can be identified in stone artifact assemblages. They studied metric variables of stone points during the introduction of bow and arrow technology in the Great Basin around AD 300-600. They equated guided transmission with high metric variation and low correlation between metric attributes, and equated model-based bias with less variation and more correlated variables. They found that in eastern California artifacts have poor correlations of basal width and mass, suggesting new technology was introduced and spread by guided transmission.On the other hand, in central Nevada metric variables are highly correlated, indicating that the bow and arrow was introduced and spread by model-based bias. Since Bettiniger and Eerkens studied archaeological data so they are unable to directly observe the transmission process. To test the underlying assumptions that Bettinger and Eerkens used, Mesoudi and O’Brien (2008) have conducted experiments that simulated prestige bias and guided variation, and observed results that supported Bettinger and Eerkens’ hypothesis.

Garvey

>>>>

need to add 'biological concept to archaeological usage': (Richerson and Boyd 1992)
Cultrual evolution that archaeologists adapted has three sub-categories: human behavioral ecology, phylogenetics and cultural transmission theory (Garvey 2018). Among them, we apply models and methods of cultural tranmssion to understand the technological change and socio cultural contexts.

@@

Bettinger and Eerkens (1997; 1999; 2008) have shown how these biases can be identified in stone artifact assemblages. They studied metric variables of stone points during the introduction of bow and arrow technology in the Great Basin around AD 300-600. They equated guided transmission with high metric variation and low correlation between metric attributes, and equated model-based bias with less variation and more correlated variables. They found that in eastern California artifacts have poor correlations of basal width and mass, suggesting new technology was introduced and spread by guided transmission.On the other hand, in central Nevada metric variables are highly correlated, indicating that the bow and arrow was introduced and spread by model-based bias. Since Bettiniger and Eerkens studied archaeological data so they are unable to directly observe the transmission process. 
Eerkens and Bettinger (2001) claims a robust statistical technique to compare varations within different kinds of assemblages and propose actual values of the coefficient of variation for showing whether artifacts are randomly produced (CV = 57.7 percent) or the result of planned production (CV 1.7 percent).

To test the underlying assumptions that Bettinger and Eerkens used, Mesoudi and O’Brien (2008) have conducted experiments that simulated prestige bias and guided variation, and observed results that supported Bettinger and Eerkens’ hypothesis.

Garvey (2018)
